
%--- Education

\section{\textsc{Education}}

\cventry{2017-present}{Postdoctoral researcher}{University of Massachusetts at Amherst}{United States of America}{}{}
\cvitem{}{Postdoctoral advisor: Dr. Verena Mart\'{i}nez Outschoorn}

\cventry{2015-2017}{Postdoctoral researcher}{University of Illinois at Urbana-Champaign}{United States of America}{}{}
\cvitem{}{Postdoctoral advisor: Dr. Verena Mart\'{i}nez Outschoorn}

\cventry{2011-2015}{Ph.D. in High Energy Physics}{Institut de F\'{i}sica d'Altes Energies (IFAE)}{Universitat Aut\`{o}noma de Barcelona}{Spain}{}
\cvitem{}{Advisor: Dr. Mario Mart\'{i}nez P\'{e}rez}
\cvitem{}{Thesis: \textit{Search for new phenomena in jets plus missing transverse energy final states at the LHC}}

\cventry{2010-2012}{M.S. in High Energy Physics, Astrophysics and Cosmology}{Institut de F\'{i}sica d'Altes Energies (IFAE)}{Universitat Aut\`{o}noma de Barcelona}{Spain}{}
\cvitem{}{Advisor: Dr. Sebasti\'{a}n Grinstein}
\cvitem{}{Thesis: \textit{New pixel sensor technologies for the ATLAS upgrade}}

\cventry{2006-2010}{B.S in Physics}{Facultat de ci\`{e}ncies}{Universitat Aut\`{o}noma de Barcelona}{Spain}{}
\cvitem{}{Advisor: Dr. John Calsamiglia Costa}
\cvitem{}{Thesis: \textit{Locality and separability in discrimination of quantic hypotheses}}

\closesection{}

%--- Employment and research

\section{\textsc{Employment and research}}

\cventry{March 2015}{Postdoctoral researcher}{CERN}{Geneva}{ATLAS Experiment}{}
\cvitem{}{Data analysist for the ATLAS Collaboration in the Higgs group. 
}
\cvitem{}{
\begin{itemize}
	\setlength{\itemsep}{5pt}
	\setlength{\topsep}{5pt}
\item Main analyzer and editor in the search for Higgs boson produced in association to a $W$ boson and decaying to four $b$-quarks via two spin-zero particles.
\item Analizer and editor in the search for Higgs boson decaying to four muons via two new spin-zero or spin-one particles.
\item Flavor-tagging contact for the Higgs Beyond the Standard Model ATLAS group.
\item Higgs Light Resonance coordinator.
\item ATLAS contact to theorititians for models of Exotic Higgs decays.
\end{itemize}}

%---
\cventry{Jul 2011-2015}{Graduate Student}{CERN}{Geneva}{ATLAS Experiment}{}
\cvitem{}{Data analysist for the ATLAS Collaboration in the SUSY and Exotics Working Groups. 
}

\cvitem{}{
\begin{itemize}
	\setlength{\itemsep}{5pt}
	\setlength{\topsep}{5pt}
\item Participation in the optimization studies for the LHC run-II.
\item Participation in the SUSY third generation Legacy Paper, intended to be a reference for the constraints placed by ATLAS with the run-I dataset. Statistical combinations as well as new interpretations have been provided based on the monojet analysis.
\item Reinterpretation of the monojet stop and sbottom searches in terms of other supersymmetric and exotic scenarios with A.Cort\'{e}s, V.Giangiobbe, C.Fischer and M.Mart\'{i}nez.
\item Main analyzer for the monojet analysis regarding the searches for third-generation squarks decaying in compressed supersymmetric scenarios.
\item Main analyzer for the monojet analysis concerning the search for pair-produced top squarks decaying into charm quarks and the lightest neutralinos.
\item Participation in the search for dark matter candidates and large extra dimensions in events with a jet and missing transverse momentum at 7~TeV.
\item Together with a post doc in our team, perform the full analysis in the searches for dark matter candidates and large extra dimensions at 7~TeV monophoton analysis.
\end{itemize}}

\cvitem{}{\hfill \newline \begin{itemize}
	\setlength{\itemsep}{5pt}
	\setlength{\topsep}{5pt}
\item Participation in the TileCal upgrade R\&D task force in the ATLAS cavern.
\item Participation as on-line data acquisition contact person for the hadronic calorimeter during operation.
\item Maintenance of the online code that processes the information from the anode integrated minimum bias currents in the ATLAS Tile Calorimeter.
\end{itemize}}

\cventry{Sep 2010-Jan 2012}{Undergraduate Research Assistant}{Institut de F\'{i}sica d'Altes Energies (IFAE)}{Spain}{}{}
\cvitem{}{\begin{itemize}
\item Research on new radiation-hard pixel sensor technologies in collaboration with CNM-Barcelona. New results of the characterization and beam test studies of n-in-p planar and 3D double sided devices bump bonded to the current ATLAS pixel front-end chip (FE-I3) were performed.
\end{itemize}}

\cventry{Aug 2010}{Summer Student}{CERN}{Geneva}{ATLAS Experiment}{}
\cvitem{}{\begin{itemize}
\item Participation in the ATLAS exotics mono jet analysis.
\end{itemize}}

\closesection{}


%--- List of significant publications

\section{\textsc{List of significant publications}}

\cvitem{}{(A complete list of publications (+150) is available at {\color{blue} \href{http://inspirehep.net/search?p=find+a+caminal}{inspirehep.net}})}


\subsection{Papers}

\cventry{}{LHC Higgs Cross Section Working Group}{}{Handbook of LHC Higgs Cross Sections: 4. Deciphering the Nature of the Higgs Sector}{FERMILAB-FN-1025-T, CERN-2017-002-M [arXiv:1610.07922 [hep-ex]]}{}

\cventry{}{ATLAS Collaboration}{}{Search for the Higgs boson produced in association with a $W$~boson and decaying to four $b$~quarks via two spin-zero particles in $pp$ collisions at 13~TeV with the ATLAS detector}{Eur.Phys.J. C76 (2016) no.11, 605 [arXiv:1606.08391 [hep-ex]]}{}

\cventry{}{ATLAS Collaboration}{}{Search for pair-produced third-generation squarks decaying via charm quarks or in compressed supersymmetric scenarios in $pp$ collisions at $\sqrt{s}=8~$TeV with the ATLAS detector}{Phys. Rev. D. 90, 052008 (2014)}{}

\cventry{}{ATLAS Collaboration}{}{Search for dark matter candidates and large extra
    dimensions in events with a photon and missing transverse momentum in $pp$ collision data at $\sqrt{s}=7$ TeV with the ATLAS detector}{Phys.Rev.Lett.110(2013)011802, 2013}{}

\cventry{}{ATLAS Collaboration}{}{Search for dark matter candidates and large extra dimensions in events with a jet and missing transverse momentum with the ATLAS detector}{JHEP  1304 (2013) 075  [arXiv:1210.4491 [hep-ex]], 2013}{}


\subsection{Conference notes}

\cventry{}{ATLAS Collaboration}{}{Search for Higgs decays to beyond the standard model light gauge bosons in four-lepton events with the ATLAS detector at $\sqrt{s} = 13$~TeV}{ATLAS-CONF-2017-042}{}

\cventry{}{ATLAS Collaboration}{}{Search for pair-produced top squarks decaying into charm quarks and the lightest neutralinos using 20.3~fb$^{-1}$ of $pp$ collisions at $\sqrt{s} = 8$~TeV with the ATLAS detector at the LHC}{ATLAS-CONF-2013-068, 2013}{}

\cventry{}{ATLAS Collaboration}{}{Search for New Phenomena in Monojet plus Missing Transverse Momentum Final States using 10 fb$^{-1}$ of $pp$ Collisions at $\sqrt{s}=8$~TeV with the ATLAS detector at the LHC}{ATLAS-CONF-2012-147, 2013}{}

%\subsection{Internal notes}
%
%\cventry{}{R. Caminal Armadans, M. Casolino, T. Farooque, A. Juste Rozas, M. Khader, V. Mart\'{i}nez Outschoorn, W. Moon, L. Valery}{}{Direct search for exotic Higgs boson decays to two spin-zero particles in the $H\rightarrow 2a\rightarrow 4b$ channel in $Pp$ collisions at $\sqrt{s} = 13$~TeV with the ATLAS detector}{ATL-COM-PHYS-2015-1457}{}
%
%\cventry{}{R. Caminal Armadans, V. Giangiobbe, A. Cort\'{e}s-Gonz\'{a}lez, C. Fischer, M. Mart\'{i}nez-P\'{e}rez}{}{New interpretations in terms of SUSY and Exotics scenarios of the monojet-like analysis used in the third generation squark searches}{ATL-COM-PHYS-2014-895}{}
%
%\cventry{}{J. Abdallah, R. Caminal Armadans, A. Cort\'{e}s-Gonz\'{a}lez, V. Giangiobbe, T. Golling, D.H. Guest, M. Hohlfeld, M. Mart\'{i}nez-P\'{e}rez, J. Schaeffer}{}{Search for Scalar Top Quarks in final states with two charm jets and missing transverse momentum at $\sqrt{s}=8$~TeV}{ATL-COM-PHYS-2013-064}{}

\subsection{Proceedings}

\cventry{}{Roger Caminal Armadans}{on behalf of the ATLAS Collaboration}{Search for non-standard and rare decays of the Higgs boson with the ATLAS detector}{ATL-PHYS-PROC-2017-084}{}

\cventry{}{Roger Caminal Armadans}{on behalf of the ATLAS and CMS Collaborations}{Searches for supersymmetry in resonance production and R-parity violating prompt signatures with the ATLAS and CMS detectors}{Nuclear and Particle Physics Proceedings 273-275 (2016) 618-624}{}

\cventry{}{Roger Caminal Armadans}{on behalf of the ATLAS Collaboration}{Search for super-symmetric compressed scenarios in monojet-like final states using 20.3~fb$^{-1}$ of $pp$ collisions at $\sqrt{s} = 8$~TeV with the ATLAS detector at the LHC}{Nuclear and Particle Physics Proceedings 273-275 (2016) 2412-2414}{}

\cventry{}{Roger Caminal Armadans}{on behalf of the ATLAS Collaboration}{Search for pair produced top squarks decaying into a charm quark and the lightest neutralinos in pp collisions at $\sqrt{s} = 8$~TeV with the ATLAS detector at the LHC}{PoS(EPS-HEP 2013)111, 2013}{}

\cventry{}{Roger Caminal Armadans}{on behalf of the ATLAS Collaboration}{Searches for monojets and monophotons with the ATLAS detector}{PoS(DIS 2013)119, 2013}{}

\closesection{}


%--- Conferences and schools

\section{\textsc{Conferences and schools}}

\cventry{Apr 2017}{XXV International Workshop on Deep-Inelastic Scattering and Related Subjects (\href{https://indico.cern.ch/event/568360/}{DIS 2017})}{}{Birmingham}{United Kingdom}{}
\cvitem{}{
	\begin{itemize}
	\item{Talk:} Search for non-standard and rare decays of the Higgs boson with the ATLAS detector.
	\end{itemize}
}

\cventry{Oct 2014}{VI \href{http://www.i-cpan.es/jornadas6/}{CPAN} days}{}{Sevilla}{Spain}{}
\cvitem{}{
	\begin{itemize}
	\item{Talk:} Search for supersymmetry in compressed scenarios.
	\end{itemize}
	}

\cventry{Jul 2014}{37th International Conference on High Energy Physics (\href{http://ichep2014.es/}{ICHEP 2014})}{}{Valencia}{Spain}{}
\cvitem{}{
	\begin{itemize}
	\item{Talk:} Searches for supersymmetry in resonance production and R-parity violating prompt signatures with the ATLAS and CMS detectors.
	\item{Poster:} Search for pair-produced third-generation squarks in compressed supersymmetric scenarios using monojet-like final states in $pp$ collisions at $\sqrt{s} = \unit[8]{TeV}$ with the ATLAS detector at the LHC.
	\end{itemize}
	}

\cventry{Sep 2013}{Taller de Altas Energ\'{i}as 2013 (\href{http://benasque.org/2013tae/}{TAE HEP school 2013})}{}{Benasque}{Spain}{}
\cvitem{}{}

\cventry{Jul 2013}{European Physical Society Conference on High Energy Physics (\href{http://eps-hep2013.eu/}{EPS HEP 2013})}{}{Stockholm}{Sweden}{}
\cvitem{}{
	\begin{itemize}
	\item{Poster:} Search for Scalar Top Quarks in the final states with two charm jets and missing transverse momentum at $\sqrt{s} = \unit[8]{TeV}$.
	\end{itemize}
	}

\cventry{May 2013}{Large Hadron Collider Physics Conference (\href{http://lhcp2013.ifae.es/}{LHCP 2013})}{}{Barcelona}{Spain}{}
\cvitem{}{}

\cventry{Apr 2013}{XXI International Workshop on Deep-Inelastic Scattering and Related Subjects (\href{http://dis2013.in2p3.fr/}{DIS 2013})}{}{Marseille}{France}{}
\cvitem{}{
	\begin{itemize}
	\item{Talk:} Searches for monojets and monophotons with the ATLAS detector.
	\end{itemize}
	}

\closesection{}

%--- Yellow book report 4: https://arxiv.org/abs/1610.07922
%--- H->2a->4b
%--- ttH(bb)
%--- H->2a->4mu
%--- DIS conference

%\pagebreak{}
